---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  background: #1A1A1A;
  color: #FFFFFF;
  font-family: 'Helvetica', Arial, sans-serif;
  max-width: 850px;
  margin: auto;
  line-height: 1.7;
  padding: 20px;
}

/* Main Title & Headers */
h2 {
  font-weight: 500;
  font-size: 2.2rem;
  color: #2EC4B6; 
  border-bottom: 2px solid #2EC4B6;
  padding-bottom: 10px;
  margin-top: 40px;
  letter-spacing: 1px;
}

h3 {
  font-weight: 400;
  font-size: 1.5rem;
  color: #FF9F1C; /* coffee */
  margin-top: 30px;
}


p {
  font-weight: 300;
  font-size: 1.1rem;
  color: #FFFFFF;
  text-align: left;
}

strong {
  color: #2EC4B6;
  font-weight: 600;
}

/* Photos */
img {
  display: block;
  margin: 30px auto;
  box-shadow: 0 4px 15px #333; 
  border: 1px solid #333;
  max-width: 100%;
  height: auto;
}
```

## What's going on with this data?

This report preovides a live analysis of caffeine habits by connecting directly to an observational log. To ensure consistency, raw survey data is processed into standardised variables. I decided to focus on two main metrics which are:

### Total observations: 

A count of all entries to track the scale of the study.

### Average Focus:

The arithmetic mean of self-reported focus scores to measure beverages effectiveness.

As new data is logged via the Google Form created, these bar charts and summaries update in real time, which offers an evolving look at consumption patterns and their impact focus.

```{r, echo=FALSE}
# PART C
suppressPackageStartupMessages(library(tidyverse)) 

csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTcFY_j3pECqJaJl5vvJ_RXgNIGjQQgr6dBa8NCgcrK6U-aTFXIBRGRxhoYs-BKVio54KVqtdyD0BzW/pub?gid=115883477&single=true&output=csv"

logged_data <- read_csv(csv_url)

latest_data <- logged_data %>%
  rename(
    timestamp = 1,
    drink_name = 2,
    type = 3,
    servings = 4,
    time_of_day = 5,
    reason = 6,
    focus_score = 7
  )
```

```{r, echo=FALSE}
# PART D
total_observation <- nrow(latest_data)
avg_focus <- round(mean(latest_data$focus_score, na.rm = TRUE), 2)
common_time <- latest_data %>% 
  count(time_of_day) %>% 
  slice_max(n, n = 1) %>% 
  pull(time_of_day)
```

```{r, echo=FALSE}
# BAR CHART 1
ggplot(latest_data, aes(x=type, fill=type)) +
  geom_bar() +
  labs(title = "Frequency of Different Drink Types Observed",
       subtitle = paste("Based On", total_observation, "total logs"),
       x = "Drinks",
       y = "Number of Times Consumed") +
  theme_grey() +
  scale_fill_brewer(palette = "Set2") +
  theme(legend.position = "none")


#BAR CHART 2 
ggplot(latest_data, aes(x = time_of_day, fill = time_of_day)) +
  geom_bar() +
  labs(title = "Caffeine Consumption Patterns by Time of Day",
       x = "Time Period",
       y = "Count") +
  theme_grey() +
  coord_flip() + #makes word not crowded in usual bar chart / flip
  theme(legend.position = "none")
```

So far, I have recorded **`r total_observation`** total drinks. On average, the average focus score after drinking is **`r avg_focus`** out of **5**. It seems everyone including me is most likely to grab a drink during **`r common_time`**.